### 2021-10-31 publication/experiments.tex
Banter
Brevify polbooks

\begin{figure}[!h]
	\centering
	\begin{subfigure}[t]{0.32\linewidth}
			\centering
			\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{polbooks-null-1}}
			\caption{Political Books.}
			\label{fig:polbooks-null}
		\end{subfigure}
	\begin{subfigure}[t]{0.32\linewidth}
			\centering
			\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{school-null-1}}
			\caption{Primary School.}
			\label{fig:school-null}
		\end{subfigure}
	\begin{subfigure}[t]{0.32\linewidth}
			\centering
			\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{fb-null-1}}
			\caption{Facebook Egonet.}
			\label{fig:fb-null}
		\end{subfigure}
	\caption{$\theta$-samples. Dotted line is $\pm c^*$.}
\end{figure}
%
\begin{figure}[!h]
	\centering
	\begin{subfigure}[t]{0.32\linewidth}
			\centering
			\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{polbooks-accuracy-2}}
			\caption{Political Books.}
			\label{fig:polbooks-null}
		\end{subfigure}
	\begin{subfigure}[t]{0.32\linewidth}
			\centering
			\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{school-accuracy-1}}
			\caption{Primary School.}
			\label{fig:school-null}
		\end{subfigure}
	\begin{subfigure}[t]{0.32\linewidth}
			\centering
			\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{fb-accuracy-1}}
			\caption{Facebook Egonet.}
			\label{fig:fb-null}
		\end{subfigure}
	\caption{Per-block accuracy $\eta(j)$.}
\end{figure}

@@

The goal here is to 
determine whether the authors' political affiliations are a good predictor 
of the overall network structure. We choose to partition the network into $B=3$ communities as we only have this many distinct values for political affiliation (conservative, liberal or neutral).

From Figure~\ref{fig:polbooks-null} we see that all 3 blocks have a distinct political affiliation as their largest positive component.  
Furthermore, in Table~\ref{tab:results} we see that the training and test losses 
are very similar and both are low in magnitude. This is strong evidence 
that political affiliation is a very appropriate explanatory 
variable for the overall network structure.

However, from Figure~\ref{fig:polbooks-accuracy} we see that block 1 has low accuracy. 
This suggests that detected block 1 is not solely composed of ``neutral" books but also 
contains some ``liberal" and ``conservative" authors. Indeed, by examining 
Figure~\ref{fig:polbooks-graph} we see that block 1 is effectively a buffer between 
blocks 2 and 3; there are very few edges between blocks 2 and 3. It is therefore not 
surprising that some books from either side leak into block 1.
The three distinct categories may be 
too coarse a measure of political affiliation; perhaps the nominally 
``conservative" books found in block 1 are closer to the centre. 
In the absence of more granular labels, we cannot test this hypothesis. 
Nevertheless, political affiliation encoded as 3 distinct labels 
remains a fantastic predictor of network structure.

>>>>

\begin{figure}[!h]
	\centering
	\begin{subfigure}[t]{0.32\linewidth}
			\centering
			\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{polbooks-null-1}}
			\caption{Political Books.}
			\label{fig:polbooks-null}
		\end{subfigure}
	\begin{subfigure}[t]{0.32\linewidth}
			\centering
			\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{school-null-1}}
			\caption{Primary School.}
			\label{fig:school-null}
		\end{subfigure}
	\begin{subfigure}[t]{0.32\linewidth}
			\centering
			\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{fb-null-1}}
			\caption{Facebook Egonet.}
			\label{fig:fb-null}
		\end{subfigure}
	\caption{$\theta$-samples. Dotted line is $\pm c^*$.}
\end{figure}
%
\begin{figure}[!h]
	\centering
	\begin{subfigure}[t]{0.32\linewidth}
			\centering
			\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{polbooks-accuracy-2}}
			\caption{Political Books.}
			\label{fig:polbooks-accuracy}
		\end{subfigure}
	\begin{subfigure}[t]{0.32\linewidth}
			\centering
			\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{school-accuracy-1}}
			\caption{Primary School.}
			\label{fig:school-accuracy}
		\end{subfigure}
	\begin{subfigure}[t]{0.32\linewidth}
			\centering
			\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{fb-accuracy-1}}
			\caption{Facebook Egonet.}
			\label{fig:fb-accuracy}
		\end{subfigure}
	\caption{Per-block accuracy $\eta(j)$.}
\end{figure}

@@

We choose to partition the network into $B=3$ communities as we only have this many distinct values for political affiliation (conservative, liberal or neutral).
From Figure~\ref{fig:polbooks-null} we see that all 3 blocks have a distinct political affiliation as their largest positive component.  
Furthermore, in Table~\ref{tab:results} we see that the training and test losses 
are very similar and both are low in magnitude. This is strong evidence 
that political affiliation is a very appropriate explanatory 
variable for the overall network structure.

However, from Figure~\ref{fig:polbooks-accuracy} we see that block 1 has low accuracy. 
This suggests that detected block 1 is not solely composed of ``neutral" books but also 
contains some ``liberal" and ``conservative" authors. Examining 
Figure~\ref{fig:polbooks-graph}, we see the majority of paths between blocks 2 and 3 go through block 1.
Block 1 is in effect a bridge between the ``conservative'' and ``liberal'' blocks so it is unsurprising that some books from either side leak into block 1.
